Progress Report

### 2020-09-02 documentation/Optimization Work/08_27_20.tex
optimization for MMSE seems to be working some

First we consider equal power allocation at the transmitter such that after finding the first $K < N_S$ IRS channels $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$, the optimization problem

@@

	for each term in the polynomial, the hermetian of the term is also in the polynomial sum (e.g both $\mG (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$ and $ (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i}\mG^H$). Because $trace(\mH^H) = trace(\mH)^*$, the complex component of these terms will always cancel. In the case of minimizing the MSE, this means that we want to minimize the resulting real component for all of these cross terms. In order to investigate further, we decompose the problem further. Neglecting the non-cross terms and using the linearity $trace$ with respect to scaling, we can equivalently consider the problem 

@@

From problem \eqref{mse_problem_clear} it is clear that if all $\phi_{j} \; j \neq i $ are held constant, $\phi_{i}$ can be chosen as a phase which fulfills the objective function. The numerical results below indicate the impact of this optimization technique on the MSE of the IRS system described above. 

>>>>

First we consider equal power allocation at the transmitter such that after finding the first $K \leq N_S$ IRS channels $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$, the optimization problem

@@

	for each term in the polynomial, the hermetian of the term is also in the polynomial sum (e.g both $\mG (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$ and $ (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i}\mG^H$). Because $trace(\mH^H) = trace(\mH)^*$, the complex component of these terms will always cancel. In the case of minimizing the MSE, this means that we want to minimize the resulting real component for all of these cross terms. In order to investigate further, we decompose the problem further. Neglecting the non-cross terms and using the linearity of the $trace$ operator with respect to scaling, we can equivalently consider the problem 

@@

From problem \eqref{mse_problem_clear} it is clear that if all $\phi_{j} \; j \neq i $ are held constant,$\phi_{j} \; j \neq i $can be chosen as a phase which fulfills the objective function. 
For a given step of this algorithm in which $\phi_{i}$ the update is determined by a sum $\phi_{i}a + b$ and $\phi_{i}$ is chosen so at to maximize the 
complex component of the sum (which we will be canceled out by its complex conjugate.
The numerical results below indicate the impact of this optimization technique on the MSE of the IRS system described above. 
